%-------------------------
% Resume in Latex - Tailored for Apple ASE (Storage Infrastructure & Reliability)
% Based on Jake Gutierrez template | Tailored by Abhay Raj
%-------------------------
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure generated PDF is ATS-friendly
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-2pt}}
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textit{\small #2} \\
    \textit{\small #3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubSubheading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small #1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%%%%%%%%%% RESUME STARTS HERE %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%----------HEADING----------
\begin{center}
  \textbf{\Huge \scshape Abhay Raj} \\ \vspace{1pt}
  \small 8178339741 $|$ \href{mailto:abhay.byte02@gmail.com}{\underline{abhay.byte02@gmail.com}} $|$
  \href{https://linkedin.com/in/abhay-byte}{\underline{linkedin.com/in/abhay-byte}} $|$
  \href{https://github.com/abhay-byte}{\underline{github.com/abhay-byte}} $|$
  \href{https://abhay-byte.web.app/}{\underline{abhay-byte.web.app}}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
\resumeSubHeadingListStart
  \resumeItem{Software engineer with hands-on experience building backend services, containerized applications, and Linux-based developer tooling. Open-source contributor with 84 public repositories and 2.6K+ commits. Strong foundation in data structures and algorithms with 150+ LeetCode problems solved. Driven by infrastructure engineering, distributed systems, and building reliable software that serves users at scale.}
\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\resumeSubHeadingListStart
  \resumeItem{\textbf{Languages}: Go, Python, Java, Kotlin, TypeScript, JavaScript, C++, Shell, SQL}
  \resumeItem{\textbf{Infrastructure \& DevOps}: Linux Administration, Docker, Git, GitHub Actions, CI/CD, AWS, GCP}
  \resumeItem{\textbf{Data \& Algorithms}: Data Structures, Algorithms, Problem Solving, Design Patterns, Performance Optimization}
  \resumeItem{\textbf{Development Practices}: Backend Architecture, API Design, Distributed Systems, System Reliability, Automation, Code Review}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
    \resumeSubheading
    {Avalon Information Systems}{Jan 2026 -- Jun 2026}
    {Backend Developer}{New Delhi, IN}
    \resumeItemListStart
        \resumeItem{Built and optimized scalable backend services using \textbf{PHP (Laravel \& CakePHP)} for OpenEMIS — an open-source Education Management System deployed at national scale across multiple countries.}
        \resumeItem{Designed modular backend architecture handling large-scale data pipelines, concurrent user requests, and distributed deployment configurations ensuring high reliability.}
        \resumeItem{Collaborated with a global team to improve system performance, reduce latency, and enhance data processing throughput for government-level education deployments.}
    \resumeItemListEnd

    \resumeSubheading
    {Gamified}{Jul 2023 -- Sep 2023}
    {Game Developer Intern}{Remote}
    \resumeItemListStart
        \resumeItem{Developed interactive systems for 10+ game scenes using \textbf{C\# and Unity}, achieving 100\% implementation accuracy and reducing iteration cycles by 25\%.}
        \resumeItem{Refactored monolithic logic into modular, reusable component architecture — improving code maintainability and reducing system complexity by 20\%.}
        \resumeItem{Integrated cross-functional assets into a cohesive runtime environment, ensuring alignment across product, design, and engineering requirements.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

    \resumeProjectHeading{\href{https://github.com/abhay-byte/fluxlinux}{\small\textbf{fluxlinux}} $|$ \emph{Kotlin / Linux}}{}
    \resumeItemListStart
        \resumeItem{Built a \textbf{Linux environment manager} for Android enabling seamless developer tooling directly on mobile devices with automated provisioning and shell integration — 80 GitHub stars.}
        \resumeItem{Integrated cross-process communication, automated package management, and containerized tool environments for portable development workflows.}
        \resumeItem{Leveraged \textbf{Linux system internals, process management, and filesystem operations} to create a reliable runtime environment on constrained mobile hardware.}
    \resumeItemListEnd

    \resumeProjectHeading{\href{https://github.com/abhay-byte/finalbenchmark-platform}{\small\textbf{finalbenchmark-platform}} $|$ \emph{Kotlin / Java}}{}
    \resumeItemListStart
        \resumeItem{Developed a comprehensive system benchmarking Android application with 10+ performance tests, \textbf{real-time monitoring}, and \textbf{background processing} optimized for efficiency.}
        \resumeItem{Implemented thermal management, resource throttling detection, and battery-aware scheduling — 25K+ Play Store installs, 63 GitHub stars.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Guru Tegh Bahadur Institute of Technology}{New Delhi, IN}
    {B.Tech in Information Technology}{Nov 2022 -- May 2026}
    \resumeSubItem{CGPA: 8.6 $|$ JEE Mains qualified $|$ GDSC Design Department}
\resumeSubHeadingListEnd

% ----------- ACHIEVEMENTS -----------
\section{Achievements}
\resumeSubHeadingListStart
  \resumeItem{\textbf{Open Source:} 2.6K+ Commits, 275 Stars, 84 Public Repositories, 76 Followers on GitHub.}
  \resumeItem{\textbf{DSA Practice:} 150+ LeetCode, 30+ Codeforces, 200+ Coding Blocks problems — strong foundation in algorithms and data structures.}
  \resumeItem{\textbf{Google Play:} Published 5+ Android applications — 25,000+ installs, 4.2/5 average rating.}
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
