%-------------------------
% Resume in Latex
% Author  : Abhay Raj
% Target  : Google — Software Engineer, University Graduate
% Generated: May 2026
%-------------------------
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-2pt}}
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textit{\small #2} \\
    \textit{\small #3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING----------
\begin{center}
  \textbf{\Huge \scshape Abhay Raj} \\ \vspace{1pt}
  \small 8178339741 $|$ \href{mailto:abhay.byte02@gmail.com}{\underline{abhay.byte02@gmail.com}} $|$
  \href{https://linkedin.com/in/abhay-byte}{\underline{linkedin.com/in/abhay-byte}} $|$
  \href{https://github.com/abhay-byte}{\underline{github.com/abhay-byte}} $|$
  \href{https://abhay-byte.web.app/}{\underline{abhay-byte.web.app}}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
\resumeSubHeadingListStart
  \resumeItem{Computer Science graduate with 2.6K+ commits across 85+ open-source repositories (254+ stars). Strong foundation in distributed systems, Linux, and full-stack development -- building everything from Android benchmarking tools to multi-agent AI workspaces. Experience in systems programming, performance optimization, and large-scale application design.}
\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Guru Tegh Bahadur Institute of Technology}{New Delhi, IN}
    {B.Tech in Information Technology}{Nov 2022 -- May 2026}
    \resumeSubItem{CGPA: 8.41}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
    \resumeSubheading
    {Avalon Information Systems}{New Delhi, IN}
    {Backend Developer}{Jan 2026 -- Jun 2026}
    \resumeItemListStart
        \resumeItem{Built and optimized scalable backend services using PHP (Laravel \& CakePHP) for OpenEMIS, an education management system used globally for national-level student data processing.}
        \resumeItem{Designed high-performance data pipelines handling institutional records across distributed deployments, ensuring reliability and sub-second query response times.}
        \resumeItem{Collaborated with a global engineering team to enhance system architecture for large-scale data processing.}
    \resumeItemListEnd

    \resumeSubheading
    {Gamified}{Remote}
    {Game Developer Intern}{Jul 2023 -- Sep 2023}
    \resumeItemListStart
        \resumeItem{Developed and shipped 10+ game scenes with 100\% design accuracy using C\# and Unity, reducing iteration cycles by 25\% through modular refactoring.}
        \resumeItem{Refactored core game mechanics into reusable components, cutting code complexity by 20\% and improving maintainability across the codebase.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
    \resumeProjectHeading{\href{https://github.com/abhay-byte/fluxlinux}{\small\textbf{FluxLinux}} $|$ \emph{Kotlin}}{}
    \resumeItemListStart
        \resumeItem{Built a custom Linux distribution with Kotlin-based tooling. Implemented kernel-level configurations, package management, and system utilities targeting developer workflows. 72 GitHub stars.}
    \resumeItemListEnd

    \resumeProjectHeading{\href{https://github.com/abhay-byte/finalbenchmark-platform}{\small\textbf{FinalBenchmark 2}} $|$ \emph{Kotlin, Android SDK, C++, JNI}}{}
    \resumeItemListStart
        \resumeItem{Created a CPU benchmarking tool for Android with 10+ performance tests for single-core and multi-core assessment, implementing real-time thermal monitoring to prevent throttling. 63 stars on GitHub, adopted on F-Droid.}
    \resumeItemListEnd

    \resumeProjectHeading{\href{https://github.com/abhay-byte/nexus}{\small\textbf{Nexus Terminal}} $|$ \emph{Tauri, React, TypeScript, Rust}}{}
    \resumeItemListStart
        \resumeItem{Architected a multi-agent AI terminal workspace supporting 13+ coding agents side-by-side with shared MCP registry and credential inheritance for seamless agent-to-tool communication. Implemented split-pane PTY terminals, session persistence, and a Kanban task board.}
    \resumeItemListEnd

    \resumeProjectHeading{\href{https://github.com/abhay-byte/nativecode}{\small\textbf{NativeCode}} $|$ \emph{Kotlin, Android, Linux, MCP}}{}
    \resumeItemListStart
        \resumeItem{Developed a vibe coding workspace for Android bundling AI coding CLIs, desktop editors, and MCP-powered assistants with portable Linux runtimes (PRoot) and GPU acceleration.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\resumeSubHeadingListStart
  \resumeItem{\textbf{Languages}: Python, Java, Kotlin, C++, TypeScript, Rust, C, SQL}
  \resumeItem{\textbf{Tools \& Platforms}: Git, Docker, Linux/Unix, AWS, GCP, React, Node.js, Android SDK}
  \resumeItem{\textbf{Methods}: System Design, Distributed Systems, Performance Optimization, CI/CD, Multi-Agent Systems}
  \resumeItem{\textbf{Domains}: Systems Programming, Full-Stack Development, Open Source, AI/ML Engineering}
\resumeSubHeadingListEnd

%-----------AWARDS-----------
\section{Awards \& Achievements}
\resumeSubHeadingListStart
  \resumeItem{\textbf{GitHub:} 2.6K+ Commits, 254+ Stars, 85+ Repositories, 38+ Followers}
  \resumeItem{\textbf{Google Play:} 5+ published Android apps, 25,000+ installs, 4.2/5 average rating}
\resumeSubHeadingListEnd

\end{document}
