%-------------------------
% Resume in Latex
% Author  : Jake Gutierrez (template) | Updated by Abhay Raj
%-------------------------
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure generated PDF is ATS-friendly
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-2pt}}
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textit{\small #2} \\
    \textit{\small #3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubSubheading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small #1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%%%%%%%%%% RESUME STARTS HERE %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%----------HEADING----------
\begin{center}
  \textbf{\Huge \scshape Abhay Raj} \\ \vspace{1pt}
  \small 8178339741 $|$ \href{mailto:abhay.byte02@gmail.com}{\underline{abhay.byte02@gmail.com}} $|$
  \href{https://linkedin.com/in/abhay-byte}{\underline{linkedin.com/in/abhay-byte}} $|$
  \href{https://github.com/abhay-byte}{\underline{github.com/abhay-byte}} $|$
  \href{https://abhayraj-porfolio.web.app}{\underline{abhayraj-porfolio.web.app}}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
\resumeSubHeadingListStart
  \resumeItem{Agentic AI Engineer and full-stack product builder who treats LLMs as teammates, not toys. I design multi-agent workflows, build MCP-native developer tools, and ship systems that make AI feel like a real coworker. Passionate about system design, vibe coding, and the open-source ecosystem. 1.8K+ commits across 41+ repositories.}
\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\resumeSubHeadingListStart
  \resumeItem{\textbf{AI \& Agentic Engineering}: LLM Orchestration, Multi-Agent Systems, Model Context Protocol (MCP), Prompt Engineering, RAG, AI Workflows, Vibe Coding, Safe AI Usage, TensorFlow, OpenAI API, Gemini API, Streamlit}
  \resumeItem{\textbf{Languages}: Python, Rust, TypeScript, JavaScript, Java, Kotlin, C++, PHP, Shell, SQL}
  \resumeItem{\textbf{Frameworks \& Frontend}: React, Next.js, Tauri, Node.js, Express, Django, Flask, Laravel, TailwindCSS, Material-UI}
  \resumeItem{\textbf{Cloud \& DevOps}: AWS, GCP, Docker, Git, Vercel, Linux Administration, GitHub Actions, Cron Jobs}
  \resumeItem{\textbf{Mobile \& Systems}: Android SDK, Kotlin Multiplatform, JNI, PRoot, GPU Acceleration, System Design, Neovim, WSL}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
    \resumeSubheading
    {Avalon Information Systems}{Jan 2026 -- Jun 2026}
    {Backend Developer}{New Delhi, IN}
    \resumeItemListStart
        \resumeItem{Contributed to \textbf{OpenEMIS}, an open-source Education Management Information System used globally for managing student data and institutional records.}
        \resumeItem{Utilized \textbf{PHP (Laravel \& CakePHP)} to build and optimize scalable backend services for OpenEMIS Core and School modules, ensuring high performance.}
        \resumeItem{Collaborated with a global team to enhance system reliability and data processing capabilities for national-level education deployments.}
    \resumeItemListEnd

    \resumeSubheading
    {Gamified}{Jul 2023 -- Sep 2023}
    {Game Developer Intern}{}
    \resumeItemListStart
        \resumeItem{Developed and implemented user interfaces for over 10 game scenes with 100\% design accuracy using C\# and Unity, reducing iteration time by 25\%.}
        \resumeItem{Refactored core game mechanics into modular, reusable components, improving code maintainability and reducing complexity by 20\%.}
        \resumeItem{Collaborated with a team of artists and designers to integrate assets and ensure alignment with gameplay requirements.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
    \resumeProjectHeading{\href{https://github.com/abhay-byte/nexus}{\small\textbf{Nexus Terminal}} $|$ \emph{Tauri, React, TypeScript, Rust}}{}
    \resumeItemListStart
        \resumeItem{Built a multi-agent AI terminal workspace supporting 13+ coding agents (Claude Code, Codex CLI, Gemini CLI, Aider, Cline, etc.) side-by-side.}
        \resumeItem{Implemented a shared MCP (Model Context Protocol) registry and credential inheritance for seamless agent-to-tool communication.}
        \resumeItem{Architected session persistence, split-pane PTY terminals, and a Kanban task board for agentic workflow management.}
    \resumeItemListEnd

    \resumeProjectHeading{\href{https://github.com/abhay-byte/nativecode}{\small\textbf{NativeCode}} $|$ \emph{Kotlin, Android, Linux, MCP}}{}
    \resumeItemListStart
        \resumeItem{Created a vibe coding workspace for Android that bundles AI coding CLIs, desktop editors, and MCP-powered assistants.}
        \resumeItem{Integrated portable Linux runtimes (PRoot) with GPU acceleration to run VS Code, Cursor, and agentic tools on mobile hardware.}
        \resumeItem{Orchestrated local MCP servers (filesystem, GitHub, Context7, Agency Agent) for offline-first agent workflows.}
    \resumeItemListEnd

    \resumeProjectHeading{\href{https://github.com/abhay-byte/VibingIde}{\small\textbf{VibingIde}} $|$ \emph{Rust, egui, PTY, Agentic IDE}}{}
    \resumeItemListStart
        \resumeItem{Engineered an agent-first, ultra-lightweight IDE in Rust with multi-agent panels and PTY-backed process launching.}
        \resumeItem{Designed ANSI stream rendering and per-panel stdin routing to enable real-time interaction with AI CLI tools.}
        \resumeItem{Built config-driven project loading and history persistence for reproducible agent sessions.}
    \resumeItemListEnd

    \resumeProjectHeading{\href{https://github.com/abhay-byte/minor-project-gtbit}{\small\textbf{Clinico}} $|$ \emph{MERN Stack, Flutter, Python, TensorFlow}}{}
    \resumeItemListStart
        \resumeItem{Developed an AI-powered healthcare platform with a 24/7 AI companion for preliminary diagnosis and patient triage.}
        \resumeItem{Built cross-platform mobile (Flutter) and web (React) interfaces backed by a scalable Node.js/Express API layer.}
        \resumeItem{Deployed TensorFlow-based diagnostic models and secure telemedicine workflows for NGO clinic management.}
    \resumeItemListEnd

    \resumeProjectHeading{\href{https://github.com/abhay-byte/AI_WRAPPER_PROJECTS}{\small\textbf{AI Wrapper Project}} $|$ \emph{Python, Streamlit, OpenAI API, Pandas}}{}
    \resumeItemListStart
        \resumeItem{Shipped a modular AI-driven financial platform leveraging LLMs for automated report generation and market trend analysis.}
        \resumeItem{Integrated real-time news APIs and investment growth projection engines with interactive Plotly visualizations.}
        \resumeItem{Designed prompt pipelines for diversification and risk-management insights delivered via a clean Streamlit UI.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Guru Tegh Bahadur Institute of Technology}{New Delhi, IN}
    {B.Tech in Information Technology}{Nov 2022 -- May 2026}
    \resumeSubItem{CGPA: 8.41}
\resumeSubHeadingListEnd

% ----------- ACHIEVEMENTS -----------
\section{Achievements}
\resumeSubHeadingListStart
  \resumeItem{\textbf{GitHub Stats:} 1.8K+ Commits, 350+ Stars, 99+ Pull Requests, Contributed to 41+ Repositories.}
  \resumeItem{\textbf{Google Play:} Published 5+ Android applications, achieving over 25,000 installs and a 4.2/5 average rating.}
  \resumeItem{\textbf{\href{https://leetcode.com/u/abhay-byte/}{LeetCode}:} Solved 150+ problems focusing on Data Structures and Algorithms.}
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
