%------------------------- 
% Resume in Latex 
% Author  : Jake Gutierrez (template) | Updated by Abhay Raj
%------------------------- 
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{} 
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure generated PDF is ATS-friendly
\pdfgentounicode=1

%------------------------- 
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-2pt}}
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textit{\small #2} \\
    \textit{\small #3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubSubheading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small #1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%%%%%%%%%% RESUME STARTS HERE %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%----------HEADING----------
\begin{center}
  \textbf{\Huge \scshape Abhay Raj} \\ \vspace{1pt}
  \small 8178339741 $|$ \href{mailto:abhay.byte02@gmail.com}{\underline{abhay.byte02@gmail.com}} $|$
  \href{https://linkedin.com/in/abhay-byte}{\underline{linkedin.com/in/abhay-byte}} $|$
  \href{https://abhayraj-porfolio.web.app}{\underline{abhayraj-porfolio.web.app}}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
\resumeSubHeadingListStart
  \resumeItem{Developed production-ready web and mobile applications for \textbf{2,000+} users. Contributed to open-source projects, resolved software defects, and rapidly learned new technologies to address business needs.}
\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Guru Tegh Bahadur Institute of Technology}{New Delhi, IN}
    {B.Tech Information Technology}{Nov. 2022 -- May 2026}
    \resumeSubItem{Current Percentage: 80.65\%}
\resumeSubHeadingListEnd
%-----------EXPERIENCE-----------
%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {Gamified}{Jul 2023 -- Sep 2023}
    {Game Developer (Unity, C\#)}{}
    \resumeItemListStart
      \resumeItem{Developed and optimized gameplay mechanics in \textbf{Unity} using C\#, reducing frame drops by \textbf{15\%}.}
      \resumeItem{Built user interfaces for \textbf{10+} game scenes with \textbf{100\%} design accuracy, reducing iteration time by \textbf{25\%}.}
      \resumeItem{Refactored core mechanics into modular components, cutting code complexity by \textbf{20\%}.}
      \resumeItem{Collaborated with artists/designers to integrate 3D assets and animations seamlessly.}
    \resumeItemListEnd
\resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
  \resumeProjectHeading{\href{https://aiwrapper.streamlit.app/}{\small\textbf{Investment Growth Prediction} $|$ \emph{Python, Streamlit, Plotly, GenAI}}}{Apr 2025 -- May 2025}
  \resumeItemListStart
    \resumeItem{Developed an interactive dashboard simulating \textbf{10-year} portfolio growth scenarios based on user input.}
    \resumeItem{Integrated GenAI to generate personalized investment summaries, reducing manual analysis time by \textbf{70\%}.}
    \resumeItem{Provided downloadable CSV reports and Plotly charts, increasing user retention to \textbf{60\%}.}
  \resumeItemListEnd

  \resumeProjectHeading{\href{https://github.com/abhay-byte/task_management_tool}{\small\textbf{Task.Web.App} $|$ \emph{MERN, MUI, GCP}}}{Mar 2025 -- Apr 2025}
  \resumeItemListStart
    \resumeItem{Engineered a task-management platform for \textbf{25+} users, enabling tracking of \textbf{100+} tasks with an average response time under \textbf{150 ms}.}
    \resumeItem{Implemented JWT authentication and role-based access control, eliminating unauthorized access incidents.}
    \resumeItem{Visualized weekly and monthly completion rates with interactive charts, increasing user engagement by \textbf{25\%}.}
  \resumeItemListEnd

  \resumeProjectHeading{\href{https://play.google.com/store/apps/details?id=com.ivarnagames.fantasyracer}{\small\textbf{Fantasy Racing – Star Alliance} $|$ \emph{Unity, C\#, Blender}}}{2024}
  \resumeItemListStart
    \resumeItem{Developed a sci-fi racing game featuring planetary environments, power-ups, and multiplayer features.}
    \resumeItem{Integrated physics-based vehicle controls and progression systems with unlockable upgrades.}
    \resumeItem{Published on Google Play with growing user base and community engagement.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

% ----------- ACHIEVEMENTS -----------
\section{Achievements}
\resumeSubHeadingListStart
  \resumeItem{\textbf{\href{https://leetcode.com/u/abhay-byte/}{LeetCode}:} Solved over \textbf{135+} questions, earned a \textbf{50-day} streak badge, and maintained a \textbf{1409} rating.}
  \resumeItem{\textbf{\href{https://play.google.com/store/apps/dev?id=8004929841101888920&hl=en_US&gl=US}{Google Play}:} Published \textbf{5} Android apps, accumulating \textbf{25,000+} installs and a \textbf{4.2/5} average rating from \textbf{200} reviews.}
  \resumeItem{\textbf{\href{https://github.com/abhay-byte/}{GitHub}:} Maintained a \textbf{60-day} streak with over \textbf{900} commits and \textbf{70} merged PRs across \textbf{12} active repositories.}
\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\resumeSubHeadingListStart
  \resumeItem{\textbf{Programming Languages}: HTML5, CSS3, JavaScript, SQL, Python, Java, C, C++, C\#}
  \resumeItem{\textbf{Web Technologies}: Git, RESTful APIs, MySQL, Tailwind, Material-UI, React.js, Next.js, Express.js, Node.js, MongoDB, PostgreSQL}
  \resumeItem{\textbf{Game Development}: Unity, Unreal Engine, Godot, Blender}
  \resumeItem{\textbf{Developer Tools}: Nano, Docker, Neovim, JetBrains WebStorm, WSL}
  \resumeItem{\textbf{Data Science}: NumPy, Pandas, Matplotlib, Seaborn, Plotly}
  \resumeItem{\textbf{Cloud}: AWS (EC2, S3, VPC, ECS, Amplify), GCP (Compute Engine, App Engine, Cloud Storage), Vercel, Render}
  \resumeItem{\textbf{Artificial Intelligence}: Gemini, Google GenAI}
  \resumeItem{\textbf{Other}: \href{https://github.com/abhay-byte/DSA_Practice}{Data Structures and Algorithms}} 
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
